---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RTHORR

<!-- badges: start -->
<!-- badges: end -->

The goal of RTHORR is to make it simple to run a text file of correlation matrices - or raw data - through the randomization test of hypothesized order relations (RTHOR; Hubert & Arabie, 1987) and make comparisons of fit between pairs of matrices (or raw dataframes). This program is especially valuable in the evaluation of circumplex models of data as found in color perception, vocational interests, and interpersonal behavior.



Hubert, L., & Arabie, P. (1987). Evaluating order hypotheses within proximity matrices. Psychological Bulletin, 102(1), 172–178. https://doi.org/10.1037/0033-2909.102.1.172

## Installation

You can install this development version of RTHORR from [github](https://github.com/) with:

``` r
devtools::install_github("michaellynnmorris/RTHORR")
```

## Examples


```{r example}
library(RTHORR)

#run randall on input.txt
#outputs a single data frame with RTHOR results
randall_output <- RTHORR::randall(n=6,
                                  nmat=3,
                                  ord = "circular6",
                                  input=system.file("extdata", "input.txt", package = "RTHORR"),
                                  description = c("sample_one", "sample_two", "sample_three"))


#run randmf on input.txt
#outputs a list with two dataframes (RTHOR results and comparisons)
randmf_output <- RTHORR::randmf(n=6,
                                nmat=3,
                                ord = "circular6",
                                input=system.file("extdata", "input.txt", package = "RTHORR"))


#view an example of correlation matrix input
# file.edit(system.file("extdata", "input.txt", package = "RTHORR"))


```


